%!TEX root = ../main.tex

\chapter{Conclusion}
\label{sec:conclusion}

Since the discovery of \CP violation in 1964 by Christenson, Cronin, Fitch and
Turlay~\cite{CPV_discovery} there have been many experiments searching for \CP
violation, first in the sector of neutral $K$ mesons but later on also in
neutral $B$ mesons. The most significant indication of \CP violation for \Bz
mesons is found by the determination of \sintwobeta using \BdToJPsiKS decays.
But although \lhcb is not the first experiment, even not at a hadron collider,
to measure \CP violation it plays an important role in the further exploration
of the quark-mixing sector.

The measurement of \CP violation in \BdToJPsiKS
decays~\cite{LHCb-PAPER-2015-004} using proton-proton collision data
corresponding to an integrated luminosity of \SI{3}{\invfb}, which is
presented in this thesis, yields
\begin{align*}
  \SJpsiKS &=  \phantom{-}0.731 \, \pm 0.035 \, \text{(stat)} \pm 0.020 \, \text{(syst)}\,, \\
  \CJpsiKS &=  			- 0.038 \, \pm 0.032 \, \text{(stat)} \pm 0.005 \, \text{(syst)}\,,
\end{align*}
which is the most precise determination of these \CP observables at a hadron
collider to date and is almost as precise as the previous measurements by
\babar~\cite{BaBar_sin2beta} and \belle~\cite{Belle_sin2beta}. The central
values are compatible with the world averages and with the Standard Model
expectations. Thus, it serves as a benchmark measurement showing the
capability of \lhcb to perform flavour-tagged precision measurements of \CP
violation. The experimental difficulties, \eg decay time resolution,
production asymmetries and asymmetries induced by the flavour tagging, are
well under control as the result is statistically limited. The largest
systematic uncertainty on \SJpsiKS is introduced by a possible tagging
asymmetry of the background, which is not accounted for in the likelihood fit.
With an increased statistics this effect can probably be analysed, controlled
and suppressed better. Furthermore, in the meantime new same-side
flavour-tagging algorithms have been developed~\cite{LHCb-PAPER-2016-039},
which are used for the first time in the measurement of \CP violation in
\BdToDD decays~\cite{LHCb-PAPER-2016-037} yielding
\begin{align*}
  \SDD &=  -0.54 \, ^{+0.17}_{-0.16} \, \text{(stat)} \pm 0.05 \, \text{(syst)}\,, \\
  \CDD &=  \phantom{-}0.26 \, ^{+0.18}_{-0.17} \, \text{(stat)} \pm 0.02 \, \text{(syst)}\,.
\end{align*}
If the flavour-tagging performance was the same as in the \BdToJPsiKS
analysis, the 70 times lower number of available signal candidates
(\num{114000} \BdToJPsiKS decays vs. \num{1610} \BdToDD decays) would only
allow a sensitivity of \num{\pm0.29} and \num{\pm0.27} for \SDD and
\CDD, respectively. However, the kinematic properties of the selected \BdToDD
candidates lead to a significantly higher tagging power and on top of that the
usage of the improved flavour-tagging algorithms increases the tagging power
by another \SI{20}{\percent}. The latter improvement can probably be exploited
in future measurements of \sintwobeta with \BdToJPsiKS decays. The value of
\effeff = \SI{8.1}{\percent} for the \BdToDD sample is the highest tagging
power to date in a tagged \CP violation measurement at \lhcb.

The main achievement of the measurement of \CP violation in \BdToDD decays is
to constrain the contribution of higher-order Standard Model corrections to be
small. The result of
\begin{align*}
	\Delta \phid = -0.16\,^{+0.19}_{-0.21}\,\si{\radian}
\end{align*}
can be transferred to the measurement of \CP violation in \BsToDsDs
decays~\cite{LHCb-PAPER-2014-051}, where \phis, the mixing phase of the \Bs
meson sector, can be determined, but only in a sum with a phase shift $\Delta
\phis$, which shows a very similar structure to $\Delta \phid$ (see
\cref{sec:cpviolation:btoccbard}).

The analysis of \BdToDD decays is only the starting point for similar
measurements in other \allBToDD decay modes. First studies using \BdToDstD
decays have already been performed~\cite{BToDstDthesis}. Recent calculations
taking into account the flavour-tagging performance seen in \BdToDD and the
increase in statistics when adding data from Run~II indicate that the
sensitivity of \babar~\cite{Aubert:2008ah} and \belle~\cite{Rohrken:2012ta}
could be reached and even be topped.

Up to now no significant deviations from the Standard Model expectations have
been observed, neither in direct nor in indirect searches. It is obvious that
only a tiny effect corresponding to a quite high energy scale is possible. But
the question is not really if new physics is needed but rather how it looks
like. No dark matter candidate has been found so far. The origin of the
baryonic universe with the absence of antimatter can not be explained by the
amount of \CP violation incorporated in the SM. Explanations can only be found
with more data. Currently, Run~II of the \lhc is ongoing. Herein, data is
collected at an increased centre-of-mass energy of \SI{13}{\TeV}, which leads
to a higher \bbbar cross section with respect to the proton-proton collisions
recorded during Run~I, as the cross section roughly scales linearly with the
centre-of-mass energy. The same applies for direct searches at \atlas and
\cms, which can be extended to higher masses. In principle, for \lhcb the
instantaneous luminosity could also be raised to further increase the data
samples, though it is already higher than the design value originally planned
in the proposal for the detector~\cite{LHCb-Technical-Proposal}. However, a
key to significant improvements, especially for decays with hadronic final
states but also for measurements of charmonium, is the performance of the
trigger system. After the upgrade in 2018--2020 it is planned to read out the
full detector at \SI{30}{\mega\hertz}~\cite{LHCb-TDR-016}. Right now, the
signal efficiency of the hardware trigger is not higher than
\SI{50}{\percent}. Therefore, a large potential for improvements exists.
Another important aspect of tagged \CP violation measurements is the
performance of the flavour-tagging algorithms. The higher the occupancy in the
detector the more difficult it is to find the appropriate tagging particle.
There are ideas, at least for Run~II, how to accommodate for this and the
higher centre-of-mass energy helps in regaining the flavour-tagging
performance of Run~I. Additionally, in the sector of \Bz mesons the restart of
\belle~II, planned for 2017, with an improved detector should increase the
sensitivity of many measurements significantly. Only the combination of all
these efforts to increase the available amount of data to be analysed might
result in the observation of deviations from the Standard Model expectations
and thus a hint for new physics.
