%!TEX root = ../main.tex

\chapter{Introduction}
\label{sec:Introduction}

From latest measurements the age of our universe is calculated to be
\num{13.8} billion years~\cite{Ade:2015xua}. Theoretical models exist that
describe the evolution of the universe during this incredibly long period of
time, starting from directly after the Big Bang~\cite{BigBang} until today.
But although there are models describing phenomena ranging from the largest
(cosmological models) down to the smallest scales (Standard Model of particle
physics (SM)), a comprehensive model has not been found so far. One of the
most striking observations is that we are surrounded by matter, while there
are no antimatter clusters. Though, according to big bang theories at the
origin of the universe the same amount of matter and antimatter must have been
created. Sakharov has proposed three conditions~\cite{Sakharov:1967dj} that
need to be fulfilled to explain this so called baryogenesis: At some point in
the evolution of the universe the thermal equilibrium must have been imbalanced,
the baryon number conservation is required to be violated, and the $C$ (and
even \CP) symmetry has to be violated as well. While baryon number violation
has not been observed so far, \eg the lifetime of the proton is determined to
be greater than \SI{5.9e33}{years}~\cite{Abe:2014mwa}, evidence for a
violation of the thermal equilibrium has been found~\cite{ThermalEquilibrium}.
Moreover, already fifty years ago $C$-violating and shortly thereafter
\CP-violating processes have been discovered~\cite{CPV_discovery}. Still,
there are reasons why even after so many years this topic is interesting. On
the one hand, the size of \CP violation in the SM is orders of magnitude below
what is required to explain the matter-antimatter
asymmetry~\cite{Huet:1994jb}. On the other hand, \CP-violating processes are
an excellent test bed for the predictions in the quark-flavour sector of the
Standard Model of particle physics. The unitarity of the
Cabibbo-Kobayashi-Maskawa (CKM) matrix, which describes the probability of
quark transitions, is a fundamental requisite of the SM. It can be tested by
studying the unitarity triangle, which represents one of the unitarity
conditions of the CKM matrix. The determination of the angle $\beta$ of this
triangle, or more precisely of the derived quantity \sintwobeta, is the common
theme of this thesis. Precision measurements of \CP violation in charmonium
decays, \ie in decay modes involving a \ccbar resonance, and in open charm
decays, \ie in decay modes with at least one hadron containing exactly one
\cquark quark, are performed. More specifically, \CP violation is studied in
\BdToJPsiKS and in \BdToDD decays. The two analyses exploit the full Run~I
data sample, which is the world's largest sample of \Bz mesons. It corresponds
to an integrated luminosity of \SI{3}{\invfb} collected with the \lhcb
detector in proton-proton collisions at centre-of-mass energies of
\SIlist{7;8}{\TeV}. While the decay mode \BdToJPsiKS offers a very clean
determination of \sintwobeta at a very high precision, the main purpose of the
study of \BdToDD decays is to constrain higher-order Standard Model
corrections occurring in measurements of the \CP-violating phase. These
contributions need to be controlled to distinguish them from effects caused by
physics beyond the Standard Model of particle physics, often referred to as
\enquote{New Physics}. There are several reasons to believe that the SM needs
to be extended. The measurements of rotation curves of
galaxies~\cite{AndromedaNebula} have lead to the assumption of the presence of
dark matter. This is not a small effect. Around \SI{26}{\percent} of the
energy density in the universe are assigned to dark matter compared to around
\SI{5}{\percent} for normal baryonic matter~\cite{Ade:2015xua}. However, dark
matter is not accounted for in the SM, and no dark matter candidate has been
found so far. Furthermore, in the SM the neutrinos are set to be massless,
which is disproved by the observation of neutrino
oscillations~\cite{Fukuda:1998mi,Ahmad:2001an,*Ahmad:2002jz}, awarded with the
Nobel prize in 2015~\cite{NobelPrize2015}.

The thesis is structured as follows: First, the basics of the
Standard Model of particle physics are shortly introduced (see
\cref{sec:standardmodel}). In \cref{sec:cpviolation} a more detailed
description of the origin and nature of \CP violation is given as well as ways
to measure it. The \lhcb experiment, namely the detector and the associated
software, is described in \cref{sec:detector}. Some relevant techniques
applied in data analysis of high energy physics are presented in
\cref{sec:dataanalysis}. After these prerequisites are introduced, the analysis
strategies of the measurements of \CP violation in \BdToJPsiKS decays (see
\cref{sec:bd2jpsiks}) and in \BdToDD decays (see \cref{sec:b02dd}) are
discussed. The results of the two analyses are compared with previous
measurements and with each other in \cref{sec:discussion} and a summary of the
outcome of this thesis is given in \cref{sec:conclusion}.
